%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Business Analyst} % Job title
    {Technotrendz Solutions Pvt. Ltd.} % Organization
    {Faridabad, India} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed end-to-end tender documentation, including reviewing eligibility criteria, compiling technical and financial data, and ensuring accurate and timely submission in compliance with government procurement standards.}
        \item {Automated accounts payable processes by developing and implementing a system for the automated data entry of purchase invoices.}
        \item {Streamlined procurement documentation through the creation of standardized templates for both challans and purchase orders.}
      \end{cvitems}
    }

  \cventry
    {Content writer-Academic Content} % Job title
    {Content champion} % Organization
    {Faridabad, India} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed structured, concept-centric questions and corresponding solutions aligned with the NCERT Curriculum for Classes 1–10.}
        \item {Study material subsequently adopted by Edtech companies like Brainly, Vedantu, Embibe, etc.}
      \end{cvitems}
    }

  \cventry
    {Teaching Intern – Mathematics} % Job title
    {Senior secondary school} % Organization
    {Ballabhgarh, India} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted mathematics lessons for students of Classes 6 to 10 as part of a structured internship program.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
